Data preparation report

### 2023-06-09 00_dataPrepReport.Rmd
clarified UTM zone

For each individual in each season, I calculated the centroid of its
coordinates. Then I looked at some histograms of the centroids in each
season and decided that 3550000 latitude (in ITM coordinates) would be a
cutoff point that would neatly divide individuals in the southern
population from the northern population (there was a large gap in the
histogram consistently around this value).

@@

```{r remove-northern}
# Restrict to southern individuals ----------------------------------------
# Based on previous investigations for the 2022 breeding and non-breeding seasons, have found that a good cutoff for southern vs. non-southern is 3550000 (in ITM)
## Transform to SF object, so we can get centroids
seasonsSF <- map(seasons, ~.x %>%
                   sf::st_as_sf(coords = c("location_long", "location_lat"), remove = F) %>%
                   sf::st_set_crs("WGS84") %>%
                   sf::st_transform(32636))

>>>>

For each individual in each season, I calculated the centroid of its
coordinates. Then I looked at some histograms of the centroids in each
season and decided that 3550000 latitude (in UTM zone 36N coordinates--https://epsg.io/32636) would be a
cutoff point that would neatly divide individuals in the southern
population from the northern population (there was a large gap in the
histogram consistently around this value).

@@

```{r remove-northern}
# Restrict to southern individuals ----------------------------------------
# Based on previous investigations for the 2022 breeding and non-breeding seasons, have found that a good cutoff for southern vs. non-southern is 3550000 (UTM 36N, https://epsg.io/32636)
## Transform to SF object, so we can get centroids
seasonsSF <- map(seasons, ~.x %>%
                   sf::st_as_sf(coords = c("location_long", "location_lat"), remove = F) %>%
                   sf::st_set_crs("WGS84") %>%
                   sf::st_transform(32636))
